Irt plot extra

### 2022-02-16 manuscript.Rmd
Typo corrected

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey. The survey took around 15 to 20 minutes for which they were not compensated. As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants needed to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks". At first we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample). Next, we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

@@

## Analytic Strategies

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0). In the item generation and selection phase we had developed a item pool of 48 items with six-pont Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we collapsed them into one, making it a 5 point Likert type response format. We conducted an initial item analysis and proceed to the EFA with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`). Prior to the EFA, necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, For EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method- "minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the simple latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018]. We also conducted a EFA on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

For reliability estimation we used internal consistency reliability coefficient ordinal alpha. Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient value range from 0 to 1 and higher value represents better reliability.

To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with robust weighted least square (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using  CFI, TLI, SRMR and RMSEA.

Using the CFA sample (n=`r nrow(CFA.descriptives)`) we assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) using the validated latent structure obtained in CFA. MI evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015]. We used  structural equation modelling framework to assess the measurement invariance.  We successively compared four nested models:  configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$). Among MI models, configural model is the least restrictive model and residual model is the most restrictive model. A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior invariance model to be accepted. [@widaman1997exploring].

@@

Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA. We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`). IRT assess the item quality by estimating item difficulty, item discrimination, item information, and Test information [@bakerBasicsItemResponse2017]. Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. We also assessed the precision of the short LEBA using Test information curve (TIC). TIC  indicates the amount of information an the full-scale carry along the latent trait continuum. Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018]. Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit. Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].

@@

After reviewing the literature, we identified several light exposure related scale. However, no scales specifically measuring the behavioural component of light exposure were found (\@ref(tab:reltab2). As such, we developed a comprehensive item pool of 48 items. The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Our sample size exceeds these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

```{r partmap, fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 800 )
```

@@

Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`]. Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither". With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option. We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] . The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package. After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* $\ge$ `r min(desc_tibble$"**q-value**", na.rm=T)`).

@@

Table \@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. Some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions [Marida's test;[@mardiaMeasuresMultivariateSkewness1970]]. Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30. The absolute value of inter-item correlation ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:figCor) depicts the correlation matrix.

@@

corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 8),
         axis.text.y = element_text(size = 8),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 600, bg ="white")

@@

(ref:figCor) Inter item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than .30

@@

Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:factormp)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Figure \@ref(fig:EFAplot)(A) depicts the obtained five factor structure. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAplot)(B)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).

>>>>

@@

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians. The survey took around 15 to 20 minutes and participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants needed to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks". At first we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample). Next, we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021. 
## Analytic Strategies

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0). In the item generation and selection phase we had developed a item pool of 48 items with six-point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we collapsed them into one, making it a 5 point Likert type response format. We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`). Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020]. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018]. We also conducted a EFA on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

For reliability estimation we used internal consistency reliability coefficient ordinal alpha. Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors using polychoric-correlation matrix [@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient value range from 0 to 1 and higher value represents better reliability.

To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with Weighted Last Square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI, SRMR and RMSEA.

We assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) among the CFA sample (n=`r nrow(CFA.descriptives)`). MI evaluates whether a construct has the psychometric equivalence and same meaning across groups [@putnick2016measurement;@klinePrinciplesPracticeStructural2015]. We used  structural equation modelling framework to assess the measurement invariance.  We successively compared four nested models:  configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$). Among MI models, configural model is the least restrictive model and residual model is the most restrictive model. A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior invariance model to be accepted. [@widaman1997exploring].

@@

Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA. We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`). IRT assesses the item quality by estimating item discrimination, item difficulty, item information, and test information [@bakerBasicsItemResponse2017]. Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$). Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. We also assessed the precision of the short LEBA using Test information curve (TIC). TIC  indicates the amount of information an the full-scale carry along the latent trait continuum. 
Item fit and person fit of the fitted IRT models were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018]. Item fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit. Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].

@@

After reviewing the literature, we identified several light exposure related scale. However, no scales specifically measuring the behavioural component of light exposure were found (Table \@ref(tab:reltab2). As such, all authors in collaboration of an expert panel developed a comprehensive item pool of 48 items. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by the expert panel. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

```{r partmap, fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

@@

Participants in our survey aged between  `r min(desctable.data$slypos_demographics_age)`  to `r max(desctable.data$slypos_demographics_age)` years [EFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`]. In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`]. Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity. In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers. For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither". With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling. Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option. We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] . The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package. After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* $\ge$ `r min(desc_tibble$"**q-value**", na.rm=T)`).

@@

Table \@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. Some of the items were skewed with high Kurtosis values. Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`. However, no item was discarded based on descriptive statistics or item analysis.

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for conducting the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |.30|. The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:figCor) depicts the correlation matrix.

@@

corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", legend.title = "Correlation",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 8),
         axis.text.y = element_text(size = 8),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 600, bg ="white")

@@

(ref:figCor) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than |.30|

@@

Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:map)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Figure \@ref(fig:efagtPic) depicts the data distribution and endorsement pattern for the included 25 items. Figure \@ref(fig:EFAplot)(A) depicts the five factor structure obtained in EFA. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAplot)(B)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).
